---
title: "Synergistic relationship between muscle thickness, muscular strength, and functional fitness after resistance training in older women."
format: html
editor: visual
---

## Libraries

```{r}
library(rmcorr)
library(readxl)
library(reshape2)
library(lmerTest)
library(rstatix)
library(multcomp)
library(lsmeans)
library(ggpubr) 
library(ggdist)
library(car)
library(tidyr)
library(dplyr)
library(psych)
library(superb) 
library(cocor)
library(Matrix)
```

## Setting working directory

```{r}
setwd("")
```

## Loading dataset

```{r}
tidy_data1 <- readxl::read_excel("Df.xlsx", sheet = 1)
tidy_data1$Time <- as.factor(tidy_data1$Time)
```

## Descriptive statistics

First, more general characteristics:

```{r}
tidy_data1 |> 
  dplyr::group_by(Time) |> 
  dplyr::summarise(Age = format(mean(Age_), digits = 3),
                   AgeSD = format(sd(Age_), digits = 3),
                   Weight = format(mean(Weight_), digits = 3),
                   WeightSD = format(sd(Weight_), digits = 3),
                   Height = format(mean(Height_), digits = 3),
                   HeightSD = format(sd(Height_), digits = 3),
                   BMI = format(mean(BMI_), digits = 3),
                   BMISD = format(sd(BMI_), digits = 3))
```

Eating habits:

```{r}

tidy_data_eating <- readxl::read_excel("Df_eating_habits.xlsx", sheet = 1)
tidy_data_eating$Time <- as.factor(tidy_data_eating$Time)



tidy_data_eating |> 
  dplyr::group_by(Time) |> 
  dplyr::summarise(TotalEnergy = format(mean(TotalEnergy_), digits = 3),
                   TotalEnergySD = format(sd(TotalEnergy_), digits = 3),
                   RelativeEnergy = format(mean(RelativeEnergy_), digits = 3),
                   RelativeEnergySD = format(sd(RelativeEnergy_), digits = 3),
                   PtnKg = format(mean(PtnKg_), digits = 3),
                   PtnKgSD = format(sd(PtnKg_), digits = 3),
                   CHOKg_ = format(mean(CHOKg_), digits = 3),
                   CHOKgSD = format(sd(CHOKg_), digits = 3),
                   LipKg = format(mean(LipKg_), digits = 3),
                   LipKgSD = format(sd(LipKg_), digits = 3))
```

Muscle thickness:

```{r}
tidy_data1 |> 
  dplyr::group_by(Time) |> 
  dplyr::summarise(MidThighR = format(mean(MidThighThickR_), digits = 3),
                   MidThighR_SD = format(sd(MidThighThickR_), digits = 2),
                   MidThighL = format(mean(MidThighThickL_), digits = 3),
                   MidThighL_SD = format(sd(MidThighThickL_), digits = 2),
                   LatThighR = format(mean(LateralThighThickR_), digits = 2),
                   LatThighR_SD = format(sd(LateralThighThickR_), digits = 3),
                   LatThighL = format(mean(LateralThighThickL_), digits = 2),
                   LatThighL_SD = format(sd(LateralThighThickL_), digits = 2),
                   BicepsR = format(mean(BicepsThickR_), digits = 3),
                   BicepsR_SD = format(sd(BicepsThickR_), digits = 2),
                   BicepsL = format(mean(BicepsThickL_), digits = 3),
                   BicepsL_SD = format(sd(BicepsThickL_), digits = 2),
                   ThicknessSum = format(mean(ThicknessSum_), digits = 3),
                   ThicknessSumSD = format(sd(ThicknessSum_), digits = 2))
```

Muscular strength:

```{r}
tidy_data1 |> 
  dplyr::group_by(Time) |> 
  dplyr::summarise(
    ChestPress = format(mean(ChestPress_, na.rm = T), digits = 3),
    ChestPress_SD = format(sd(ChestPress_, na.rm = T), digits = 2),
    LegExtension = format(mean(LegExtension_, na.rm = T), digits = 3),
    LegExtension_SD = format(sd(LegExtension_, na.rm = T), digits = 2),
    PreacherCurl = format(mean(PreacherCurl_, na.rm = T), digits = 3),
    PreacherCurlSD = format(sd(PreacherCurl_, na.rm = T), digits = 2),
    STL = format(mean(STL_, na.rm = T), digits = 4),
    STLSD = format(sd(STL_, na.rm = T), digits = 3),
    GripStrength = format(mean(GripStrength_, na.rm = T), digits = 4),
    GripStrengthSD = format(sd(GripStrength_, na.rm = T), digits = 3))
```

Functional fitness:

```{r}
tidy_data1 |> 
  dplyr::group_by(Time) |> 
  dplyr::summarise(
    `4mGS` = format(mean(GaitSpeed_, na.rm = T), digits = 3),
    `4mGS_SD` = format(sd(GaitSpeed_, na.rm = T), digits = 2),
    TUG = format(mean(TUG_, na.rm = T), digits = 3),
    TUG_SD = format(sd(TUG_, na.rm = T), digits = 2),
    `5STS` = format(mean(STSFT_, na.rm = T), digits = 3),
    `5STS_SD` = format(sd(STSFT_, na.rm = T), digits = 2),
    `30STS` = format(mean(STS30s_, na.rm = T), digits = 3),
    `30STS_SD` = format(sd(STS30s_, na.rm = T), digits = 2),
    `6MWT ` = format(mean(SixMin_, na.rm = T), digits = 4),
    `6MWT_SD` = format(sd(SixMin_, na.rm = T), digits = 3),)
```

## Checking assumptions

Normality

```{r}
ggqqplot(tidy_data1, "ChestPress_", facet.by = "Time")
ggqqplot(tidy_data1, "LegExtension_", facet.by = "Time")
ggqqplot(tidy_data1, "PreacherCurl_", facet.by = "Time")
ggqqplot(tidy_data1, "STL_", facet.by = "Time")
ggqqplot(tidy_data1, "GripStrength_", facet.by = "Time")
ggqqplot(tidy_data1, "GaitSpeed_", facet.by = "Time")
ggqqplot(tidy_data1, "STS30s_", facet.by = "Time")
ggqqplot(tidy_data1, "STSFT_", facet.by = "Time")
ggqqplot(tidy_data1, "TUG_", facet.by = "Time")
ggqqplot(tidy_data1, "SixMin_", facet.by = "Time")
ggqqplot(tidy_data1, "MidThighThickR_", facet.by = "Time")
ggqqplot(tidy_data1, "MidThighThickL_", facet.by = "Time")
ggqqplot(tidy_data1, "LateralThickR_", facet.by = "Time")
ggqqplot(tidy_data1, "LateralThickL_", facet.by = "Time")
ggqqplot(tidy_data1, "BicepsThickR_", facet.by = "Time")
ggqqplot(tidy_data1, "BicepsThickL_", facet.by = "Time")
ggqqplot(tidy_data1, "BicepsThickness_", facet.by = "Time")
ggqqplot(tidy_data1, "LegsThickness_", facet.by = "Time")
ggqqplot(tidy_data1, "ThicknessSum_", facet.by = "Time")
```

Homogeneity of variances

```{r}
leveneTest(ChestPress_ ~ Time,  center = median, data = tidy_data1)
leveneTest(LegExtension_ ~ Time,  center = median, data = tidy_data1)
leveneTest(PreacherCurl_ ~ Time,  center = median, data = tidy_data1)
leveneTest(STL_ ~ Time, center = median, data = tidy_data1)
leveneTest(GripStrength_ ~ Time, center = median, data = tidy_data1)
leveneTest(GaitSpeed_ ~ Time, center = median, data = tidy_data1)
leveneTest(STS30s_ ~ Time, center = median, data = tidy_data1)
leveneTest(STSFT_ ~ Time, center = median, data = tidy_data1)
leveneTest(TUG_ ~ Time, center = median, data = tidy_data1)
leveneTest(SixMin_ ~ Time, center = median, data = tidy_data1)
leveneTest(TUG_ ~ Time, center = median, data = tidy_data1)
leveneTest(BicepsThickR_ ~ Time, center = median, data = tidy_data1)
leveneTest(BicepsThickL_ ~ Time, center = median, data = tidy_data1)
leveneTest(BicepsThickness_ ~ Time, center = median, data = tidy_data1)
leveneTest(MidThighThickR_ ~ Time, center = median, data = tidy_data1)
leveneTest(MidThighThickL_ ~ Time, center = median, data = tidy_data1)
leveneTest(LateralThighThickR_ ~ Time, center = median, data = tidy_data1)
leveneTest(LateralThighThickL_ ~ Time, center = mean, data = tidy_data1)
leveneTest(LegsThickness_ ~ Time, center = median, data = tidy_data1)
leveneTest(ThicknessSum_ ~ Time, center = median, data = tidy_data1)
```

## Changes from baseline to 12 and 24 weeks of RT

#### One-way ANOVA with a random intercept

General characteristics

```{r}
#Weight
Weight_model <- lme4::lmer(Weight_ ~ Time + (1|ID), data = tidy_data1) 
lmerTest::ranova(Weight_model)
Anova(Weight_model)
lsmeans(Weight_model, pairwise ~ Time, adjust = "tukey")

#BMI
BMI_model <- lme4::lmer(BMI_ ~ Time + (1|ID), data = tidy_data1) 
lmerTest::ranova(BMI_model)
Anova(BMI_model)
lsmeans(BMI_model, pairwise ~ Time, adjust = "tukey")
```

Eating habits

```{r}
#Total energy 
TotEnerg_model <- lme4::lmer(TotalEnergy_ ~ Time + (1|ID), data = tidy_data_eating) 
lmerTest::ranova(TotEnerg_model)
Anova(TotEnerg_model)
lsmeans(TotEnerg_model, pairwise ~ Time, adjust = "tukey")

#Relative energy 
RelEnerg <- lme4::lmer(RelativeEnergy_ ~ Time + (1|ID), data = tidy_data_eating) 
lmerTest::ranova(RelEnerg)
Anova(RelEnerg)
lsmeans(RelEnerg, pairwise ~ Time, adjust = "tukey")

#Relative protein
Ptn_model <- lme4::lmer(PtnKg_ ~ Time + (1|ID), data = tidy_data_eating) 
lmerTest::ranova(Ptn_model)
Anova(Ptn_model)
lsmeans(Ptn_model, pairwise ~ Time, adjust = "tukey")

#Relative CHO
CHO_model <- lme4::lmer(CHOKg_ ~ Time + (1|ID), data = tidy_data_eating) 
lmerTest::ranova(CHO_model)
Anova(CHO_model)
lsmeans(CHO_model, pairwise ~ Time, adjust = "tukey")


#Relative lipids
Lip_model <- lme4::lmer(LipKg_ ~ Time + (1|ID), data = tidy_data_eating) 
lmerTest::ranova(Lip_model)
Anova(Lip_model)
lsmeans(Lip_model, pairwise ~ Time, adjust = "tukey")
```

Muscle thickness

```{r}
# Right mid Thickness
RmidlegThick <- lme4::lmer(MidThighThickR_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(RmidlegThick)
Anova(RmidlegThick)
lsmeans(RmidlegThick, pairwise ~ Time, adjust = "tukey")

# Left mid Thickness
LmidlegThick <- lme4::lmer(MidThighThickL_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(LmidlegThick)
Anova(LmidlegThick)
lsmeans(LmidlegThick, pairwise ~ Time, adjust = "tukey")

# Right lat Thickness
RlatlegThick <- lme4::lmer(LateralThighThickR_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(RlatlegThick)
Anova(RlatlegThick)
lsmeans(RlatlegThick, pairwise ~ Time, adjust = "tukey")

# Left lat Thickness
LlatlegThick <- lme4::lmer(LateralThighThickL_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(LlatlegThick)
Anova(LlatlegThick)
lsmeans(LlatlegThick, pairwise ~ Time, adjust = "tukey")

# Right front arm Thickness
RbicepThick <- lme4::lmer(BicepsThickR_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(RbicepThick)
Anova(RbicepThick)
lsmeans(RbicepThick, pairwise ~ Time, adjust = "tukey")

# Left front arm Thickness
LbicepThick <- lme4::lmer(BicepsThickL_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(LbicepThick)
Anova(LbicepThick)
lsmeans(LbicepThick, pairwise ~ Time, adjust = "tukey")

# Legs Thickness 
LegsTotal <- lme4::lmer(LegsThickness ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(LegsTotal)
Anova(LegsTotal)
lsmeans(LegsTotal, pairwise ~ Time, adjust = "tukey")

# Biceps Thickness
BicepsTotal <- lme4::lmer(BicepsThickness ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(BicepsTotal)
Anova(BicepsTotal)
lsmeans(BicepsTotal, pairwise ~ Time, adjust = "tukey")

#Sum of Thickness
ThickSum <- lme4::lmer(ThicknessSum_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(ThickSum)
Anova(ThickSum)
lsmeans(ThickSum, pairwise ~ Time, adjust = "tukey")
```

Muscular strength

```{r}
#Chest press 1RM
Chest_model <- lme4::lmer(ChestPress_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(Chest_model)
Anova(Chest_model)
lsmeans(Chest_model, pairwise ~ Time, adjust = "tukey")

#Leg extension 1RM
LegExten_model <- lme4::lmer(LegExtension_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(LegExten_model)
Anova(LegExten_model)
lsmeans(LegExten_model, pairwise ~ Time, adjust = "tukey")

#Preacher curl 1RM
PreacherCurl_model <- lme4::lmer(PreacherCurl_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(PreacherCurl_model)
Anova(PreacherCurl_model)
lsmeans(PreacherCurl_model, pairwise ~ Time, adjust = "tukey")

#STL 1RM
STL_model <- lme4::lmer(STL_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(STL_model)
Anova(STL_model)
lsmeans(STL_model, pairwise ~ Time, adjust = "tukey")

#Grip strength
Grip_model <- lme4::lmer(GripStrength_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(Grip_model)
Anova(Grip_model)
lsmeans(Grip_model, pairwise ~ Time, adjust = "tukey")
```

Functional fitness

```{r}
#Gait speed
Gait_model <- lme4::lmer(GaitSpeed_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(Gait_model)
Anova(Gait_model)
lsmeans(Gait_model, pairwise ~ Time, adjust = "tukey")

#TUG 
TUG_model <- lme4::lmer(TUG_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(TUG_model)
Anova(TUG_model)
lsmeans(TUG_model, pairwise ~ Time, adjust = "tukey")

#5STS 
STSFT_model <- lme4::lmer(STSFT_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(STSFT_model)
Anova(STSFT_model)
lsmeans(STSFT_model, pairwise ~ Time, adjust = "tukey")

#30STS
STS30_model <- lme4::lmer(STS30s_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(STS30_model)
Anova(STS30_model)
lsmeans(STS30_model, pairwise ~ Time, adjust = "tukey")

#Six minutes walk
SixMin_model <- lme4::lmer(SixMin_ ~ Time + (1|ID), data = tidy_data1)
lmerTest::ranova(SixMin_model)
Anova(SixMin_model)
lsmeans(SixMin_model, pairwise ~ Time, adjust = "tukey")

```

## Correlations

#### Pearson's' correlation coefficient in the baseline

```{r}
Baseline <- tidy_data1 |> 
  dplyr::filter(Time == 0) #Object created to make baseline comparisons


#Strength
cor.test(Baseline$BicepsThickness_, Baseline$ChestPress_, method = "pearson")
cor.test(Baseline$LegsThickness_, Baseline$LegExtension_, method = "pearson")
cor.test(Baseline$BicepsThickness_, Baseline$PreacherCurl_, method = "pearson")
cor.test(Baseline$ThicknessSum_, Baseline$STL_, method = "pearson")
cor.test(Baseline$BicepsThickness_, Baseline$GripStrength_, method = "pearson")

#Functional fitness
cor.test(Baseline$LegsThickness_, Baseline$GaitSpeed_, method = "pearson")
cor.test(Baseline$LegsThickness_, Baseline$STS30s_, method = "pearson")
cor.test(Baseline$LegsThickness_, Baseline$STSFT_, method = "pearson")
cor.test(Baseline$LegsThickness_, Baseline$TUG_, method = "pearson")
cor.test(Baseline$LegsThickness_, Baseline$SixMin_, method = "pearson")
```

#### Pearson's' correlation coefficient between deltas

```{r}
#Changing to wide format and excluding unnecessary variables

Wide <- tidy_data1  |> 
  dplyr::select(ID, Time, 
                ChestPress_, LegExtension_,PreacherCurl_, STL_, GripStrength_,
                BicepsThickness_, LegsThickness_, ThicknessSum_,
                GaitSpeed_, TUG_, STSFT_, STS30s_, SixMin_) |> 
  pivot_wider(names_from = Time,
              values_from = c(ChestPress_, LegExtension_,PreacherCurl_, 
                              STL_, GripStrength_,BicepsThickness_, 
                              LegsThickness_, ThicknessSum_,GaitSpeed_,
                              TUG_, STSFT_, STS30s_, SixMin_),
              id_cols = ID) |>  
  rowwise() |> 
  dplyr::mutate(DeltaArmsThick = BicepsThickness__2 - BicepsThickness__0,
                DeltaLegsThick = LegsThickness__2 - LegsThickness__0,
                DeltaThickSum = ThicknessSum__2 - ThicknessSum__0,
                DeltaChest = ChestPress__2 - ChestPress__0,
                DeltaLegExt = LegExtension__2 - LegExtension__0,
                DeltaPreacher = PreacherCurl__2 - PreacherCurl__0,
                DeltaSTL = STL__2 - STL__0,
                DeltaGrip = GripStrength__2 - GripStrength__0,
                DeltaGait = GaitSpeed__2 - GaitSpeed__0,
                DeltaTUG = TUG__2 - TUG__0,
                DeltaSTSfive = STSFT__2 - STSFT__0,
                DeltaSTSthirty = STS30s__2 - STS30s__0,
                DeltaSixMin = SixMin__2 - SixMin__0)


# Strength
cor.test(Wide$DeltaArmsThick, Wide$DeltaChest, method = "pearson")
cor.test(Wide$DeltaLegsThick, Wide$DeltaLegExt, method = "pearson")
cor.test(Wide$DeltaArmsThick, Wide$DeltaPreacher, method = "pearson")
cor.test(Wide$DeltaThickSum, Wide$DeltaSTL, method = "pearson")
cor.test(Wide$DeltaArmsThick, Wide$DeltaGrip, method = "pearson")

#Functional fitness
cor.test(Wide$DeltaLegsThick, Wide$DeltaGait, method = "pearson")
cor.test(Wide$DeltaLegsThick, Wide$DeltaTUG, method = "pearson")
cor.test(Wide$DeltaLegsThick, Wide$DeltaSTSfive, method = "pearson")
cor.test(Wide$DeltaLegsThick, Wide$DeltaSTSthirty, method = "pearson")
cor.test(Wide$DeltaLegsThick, Wide$DeltaSixMin, method = "pearson")
```

#### Repeated measures correlation

Muscular strength

```{r}
# Chest press

RM_Chest <- rmcorr::rmcorr(participant = ID, measure1 = ChestPress_, 
                           measure2 = BicepsThickness_, dataset = tidy_data1)
RM_Chest

# Leg press

RM_Leg <- rmcorr::rmcorr(participant = ID, measure1 = LegExtension_, 
                         measure2 = LegsThickness_, dataset = tidy_data1)
RM_Leg

# Preacher curl

RM_Preacher <- rmcorr::rmcorr(participant = ID, measure1 = PreacherCurl_, 
                              measure2 = BicepsThickness_, dataset = tidy_data1)
RM_Preacher

# STL

RM_STL <- rmcorr::rmcorr(participant = ID, measure1 = STL_, 
                         measure2 = ThicknessSum_, dataset = tidy_data1)
RM_STL

# Handgrip strength

RM_Grip <- rmcorr::rmcorr(participant = ID, measure1 = GripStrength_,
                          measure2 = BicepsThickness_, dataset = tidy_data1)
RM_Grip
```

Functional fitness

```{r}
# 4 meter walk test


RM_Gait <- rmcorr::rmcorr(participant = ID, measure1 = GaitSpeed_, 
                             measure2 = LegsThickness_, dataset = tidy_data1)
RM_Gait

# TUG

RM_TUG <- rmcorr::rmcorr(participant = ID, measure1 = TUG_, 
                          measure2 = LegsThickness_, dataset = tidy_data1)
RM_TUG

# SLVC

RM_STSfive <- rmcorr::rmcorr(participant = ID, measure1 = STSFT_, 
                           measure2 = LegsThickness_, dataset = tidy_data1)
RM_STSfive

# 30sCS

RM_STSthirty <- rmcorr::rmcorr(participant = ID, measure1 = STS30s_, 
                            measure2 = LegsThickness_, dataset = tidy_data1)
RM_STSthirty


RM_Sixmin <- rmcorr::rmcorr(participant = ID, measure1 = SixMin_, 
                           measure2 = LegsThickness_, dataset = tidy_data1)
RM_Sixmin

```

## Comparing correlations with cocor package

#### Chest press

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.63, r.jh = 0.71, r.kh = 0.86, n = 60, 
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = 0.71, r.jh = -0.005, r.kh = 0.07, n = 60, 
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.63, r.jh = -0.005, r.kh = 0.86, n = 60, 
                         test = "meng1992")
```

#### Leg extension

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.56, r.jh = 0.51, r.kh = 0.95, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = 0.51, r.jh = 0.16, r.kh = 0.04, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.56, r.jh = 0.16, r.kh = 0.04, n = 60,
                         test = "meng1992")
```

#### Preacher curl

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.54, r.jh = 0.78, r.kh = 0.93, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = 0.78, r.jh = 0.29, r.kh = 0.46, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.54, r.jh = 0.29, r.kh = 0.46, n = 60,
                         test = "meng1992")
```

#### STL

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.65, r.jh = 0.69, r.kh = 0.95, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = 0.69, r.jh = 0.22, r.kh = 0.22, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.65, r.jh = 0.22, r.kh = 0.22, n = 60,
                         test = "meng1992")
```

#### Handgrip strength

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.27, r.jh = 0.61, r.kh = 0.96, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = 0.61, r.jh = 0.11, r.kh = 0.11, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.27, r.jh = 0.11, r.kh = 0.11, n = 60,
                         test = "meng1992")
```

#### 4mGS - Gait speed

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.06, r.jh = -0.35, r.kh = 0.77, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = -0.35, r.jh = 0.20, r.kh = -0.04, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.06, r.jh = 0.20, r.kh = -0.67, n = 60,
                         test = "meng1992")
```

#### TUG

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = -0.04, r.jh = -0.41, r.kh = 0.87, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = -0.41, r.jh = 0.14, r.kh = -0.11, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = -0.04, r.jh = 0.14, r.kh = -0.59, n = 60,
                         test = "meng1992")
```

#### 5STS

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = -0.06, r.jh = -0.45, r.kh = 0.90, n = 60,
                         test = "meng1992")
#Mcorr and deltas
cocor.dep.groups.overlap(r.jk = -0.45, r.jh = -0.08, r.kh = -0.02, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = -0.06, r.jh = -0.08, r.kh = -0.26, n = 60,
                         test = "meng1992")
```

#### 30STS

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.13, r.jh = 0.27, r.kh = 0.90, n = 60,
                         test = "meng1992")
#Mcorr and deltas 
cocor.dep.groups.overlap(r.jk = -0.13, r.jh = 0.27, r.kh = -0.02, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = -0.13, r.jh = 0.13, r.kh = -0.26, n = 60,
                         test = "meng1992")
```

#### 6MWT

```{r}
#Mcorr and baseline
cocor.dep.groups.overlap(r.jk = 0.05, r.jh = 0.42, r.kh = 0.88, n = 60,
                         test = "meng1992")
#Mcorr and deltas 
cocor.dep.groups.overlap(r.jk = 0.02, r.jh = 0.42, r.kh = -0.11, n = 60,
                         test = "meng1992")
#Baseline and deltas
cocor.dep.groups.overlap(r.jk = 0.02, r.jh = 0.05, r.kh = -0.26, n = 60,
                         test = "meng1992")
```

## Creating the repeated measures regression models (i.e., LMM)

#### Muscular strength

```{r}
ChestRegression <- lmerTest::lmer(ChestPress_ ~ BicepsThickness_ + BMI_ + 
                                    Age_ + (1| ID), REML = F, data = tidy_data1)
summary(ChestRegression)
confint(ChestRegression, level = 0.95)
effectsize::t_to_r(t = 11.384, df_error = 179.94296) #Effect size by r
car::vif(ChestRegression)


LegRegression <- lmerTest::lmer(LegExtension_ ~ LegsThickness_ + BMI_ + 
                                  Age_ + (1| ID), REML = F, data = tidy_data1)
summary(LegRegression)
confint(LegRegression, level = 0.95)
effectsize::t_to_r(t = 7.762, df_error = 168.6280) #Effect size by r
car::vif(LegRegression)


BicepsRegression <- lmerTest::lmer(PreacherCurl_ ~ BicepsThickness_ + BMI_ +
                                     Age_ + (1| ID), REML = F, data = tidy_data1)
summary(BicepsRegression)
confint(BicepsRegression, level = 0.95)
effectsize::t_to_r(t = 14.922, df_error = 167.3576) #Effect size by r
car::vif(BicepsRegression)


STLRegression <- lmerTest::lmer(STL_ ~ ThicknessSum_ + BMI_ + 
                                  Age_ + (1| ID), REML = F, data = tidy_data1)
summary(STLRegression)
confint(STLRegression, level = 0.95)
effectsize::t_to_r(t = 10.672, df_error = 147.2536) #Effect size by r
car::vif(STLRegression)


HSRegression <- lmerTest::lmer(GripStrength_ ~ BicepsThickness_ + BMI_ +
                                 Age_ + (1| ID), REML = F, data = tidy_data1)
summary(HSRegression)
confint(HSRegression, level = 0.95)
effectsize::t_to_r(t = 9.361, df_error = 137.18801) #Effect size by r
car::vif(HSRegression)
```

#### Functional fitness

```{r}
GaitRegression <- lmerTest::lmer(GaitSpeed_ ~ LegsThickness_ + BMI_ + 
                                   Age_ + (1| ID), REML = F, data = tidy_data1)
summary(GaitRegression)
confint(GaitRegression, level = 0.95)
effectsize::t_to_r(t = -2.960, df_error = 94.011442) #Effect size by r
car::vif(GaitRegression)


TUGRegression <- lmerTest::lmer(TUG_ ~ LegsThickness_ + BMI_ + 
                                  Age_ + (1| ID), REML = F, data = tidy_data1)
summary(TUGRegression)
confint(TUGRegression, level = 0.95)
effectsize::t_to_r(t = -3.486, df_error = 87.10843) #Effect size by r
car::vif(TUGRegression)


STSFTRegression <- lmerTest::lmer(STSFT_ ~ LegsThickness_ + BMI_ +
                                    Age_ + (1| ID), REML = F, data = tidy_data1)
summary(STSFTRegression)
confint(STSFTRegression, level = 0.95)
effectsize::t_to_r(t = -4.982, df_error = 165.350993) #Effect size by r
car::vif(STSFTRegression)


STS30sRegression <- lmerTest::lmer(STS30s_ ~ LegsThickness_ + BMI_ +
                                     Age_ + (1| ID), REML = F, data = tidy_data1)
summary(STS30sRegression)
confint(STS30sRegression, level = 0.95)
effectsize::t_to_r(t = 3.939, df_error = 176.14768) #Effect size by r 
car::vif(STS30sRegression)


SixRegression <- lmerTest::lmer(SixMin_ ~ LegsThickness_ + BMI_ +
                                  Age_ + (1| ID), REML = F, data = tidy_data1)
summary(SixRegression)
confint(SixRegression, level = 0.95)
effectsize::t_to_r(t = 4.736, df_error = 138.175) #Effect size by r
car::vif(SixRegression)
```

## Example of the repeated measures correlation plots

```{r}
plot(RM_Gait, tidy_data1, overall = F, lwd = 1.4, xlab = "", ylab = "", font = 1)
title(ylab = expression("KE "[SUM]*" (cm)"), line=2.2, cex.lab=1.4)
title(xlab="4-meter-gait speed (s)", line=2.2, cex.lab=1.4)
text(4.2, 21, cex=1.0, adj = 1, (italic(r[rm])~"= -0.353"))
text(4.2, 20.3, cex=1.0, adj = 1, (italic(P)~"< 0.001"))
text(2.4, 21.2, cex=2.0, adj = 1, ("a"))
```

## Creating the repeated measures mediation models (1-1-1 mediation)

#### Muscular strength

```{r}
#Chest press ###

Chest_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000, 
  L2ID="ID", X="Time", Y="ChestPress_",
  M="BicepsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(Chest_mediation, type = c("indirect"))
summary(Chest_mediation$model)

Total_eff <- lmerTest::lmer(ChestPress_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#Leg extension ###

Leg_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="LegExtension_",
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(Leg_mediation, type = c("indirect"))
summary(Leg_mediation$model)

Total_eff <- lmerTest::lmer(LegExtension_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#Preacher curl ###

Preacher_mediation<-boot.modmed.mlm.custom(
tidy_data1, nrep=1000, 
L2ID="ID", X="Time", Y="PreacherCurl_",
M="BicepsThickness_",
boot.type ="case2",
na.action = na.omit,
control = list(msMaxIter = 1000, msMaxEval = 1000),
seed=1234)

extract.boot.modmed.mlm(Preacher_mediation, type = c("indirect"))
summary(Preacher_mediation$model)

Total_eff <- lmerTest::lmer(PreacherCurl_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


# Total strength ###

STL_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000, 
  L2ID="ID", X="Time", Y="STL_", 
  M="ThicknessSum_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(STL_mediation, type = c("indirect"))
summary(STL_mediation$model)

Total_eff <- lmerTest::lmer(STL_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#Handgrip ###

Grip_mediation<-boot.modmed.mlm.custom(
tidy_data1, nrep=1000,
L2ID="ID", X="Time", Y="GripStrength_",
M="BicepsThickness_",
boot.type ="case2",
na.action = na.omit,
control = list(msMaxIter = 1000, msMaxEval = 1000),
seed=1234)

extract.boot.modmed.mlm(Grip_mediation, type = c("indirect"))
summary(Grip_mediation$model)

Total_eff <- lmerTest::lmer(GripStrength_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)
```

#### Functional fitness

```{r}
# Gait speed ###

Gait_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="GaitSpeed_", 
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)


extract.boot.modmed.mlm(Gait_mediation, type = c("indirect"))
summary(Gait_mediation$model)

Total_eff <- lmerTest::lmer(GaitSpeed_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#TUG ###

TUG_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="TUG_",
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)


extract.boot.modmed.mlm(TUG_mediation, type = c("indirect"))
summary(TUG_mediation$model)

Total_eff <- lmerTest::lmer(TUG_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#5STS

STSFT_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="STSFT_",
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(STSFT_mediation, type = c("indirect"))
summary(STSFT_mediation$model)

Total_eff <- lmerTest::lmer(STSFT_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#STS30s_ ###

STS30s_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="STS30s_",
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(STS30s_mediation, type = c("indirect"))
summary(STS30s_mediation$model)

Total_eff <- lmerTest::lmer(STS30s_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)


#Six min walk ###

SixMin_mediation<-boot.modmed.mlm.custom(
  tidy_data1, nrep=1000,
  L2ID="ID", X="Time", Y="SixMin_",
  M="LegsThickness_",
  boot.type ="case2",
  na.action = na.omit,
  control = list(msMaxIter = 1000, msMaxEval = 1000),
  seed=1234)

extract.boot.modmed.mlm(SixMin_mediation, type = c("indirect"))
summary(SixMin_mediation$model)

Total_eff <- lmerTest::lmer(SixMin_ ~ Time + (1 + Time| ID), data = tidy_data1)
summary(Total_eff)
confint(Total_eff)
```
